### 2015-02-02 paper/model.tex
revising model.tex

@@

In this equation, the actual received signal strength is attenuated by two sources: the path loss $P_d$ 
is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while 
interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers.

where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.

>>>>

The actual received signal strength is attenuated by two sources: the path loss $P_d$ is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while 
interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.  $P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers proportional to $N_t$, the number of other vehicles already connected to tower $t$.

The eRSS can then be calculated as a function of the parameter vector $\phi = \{$interference, hysteresis, load balancing$\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of handoff dynamics in the presence of RF noise on route flow estimation.

@@
